Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-14 sections/acknowledgements.tex
Removed redundant things in acknowledgements
Updating grants section

\noindent Special thanks to these people for providing us the data necessary for our project:

% Come back and indent and make parentheses affiliations
\begin{enumerate}
    \item Scott Austin, Ph.D. (Director of Astronomical Facilities, Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas) 
    \item Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator)
    \item Shane Ayotte. (UCA Mathematics Student)
\end{enumerate}

>>>>

\noindent Special thanks to Scott Austin, Ph.D. (Director of Astronomical Facilities, Associate Professor of Astronomy and Physics, Department of Physics, Astronomy, and Engineering, University of Central Arkansas), Todd Abel, Ph.D. (UCA STEM Institute Co-Director, Associate Professor of Mathematics, Secondary Mathematics Education Program Coordinator), and Shane Ayotte. (UCA Mathematics Student)

This research would not have been possible without the support of state and federal research grants. Funding to purchase the radio telescope came from the Arkansas Space Grant Consortium (ASGC) Statewide Equipment Award, grant number GR013133-22-UCA. Funding to support student research and travel to present our results came from the Arkansas Space Grant Consortium (ASGC) Student Intensive Training award, grant number 242040-25.UCA.SIT.Lusk, a subaward of NASA award number 80NSSC20M0106.
